Learning how to act: making good decisions with machine learning

### 2017-09-10 thesis/offcuts_chapter6.tex
fixed grammer issues

\section{Philosophical objections to counterfactuls}
There are complex philosophical objections to counterfactuals arising from the way they describe alternate universes that were never realised. This makes it quite easy to (accidentally) make statements about counterfactuals that cannot be tested with empirical data. Consider the following example based on \citet{Dawid2000}. Again we have a drug where the outcome for an individual if treated is represented by the counterfactual variable $\cf{Y}{1}$ and the outcome if not treated is $\cf{Y}{0}$. Suppose these counterfactual variables $\cf{Y}{1}$ and $\cf{Y}{0}$ are jointly normal with equal variance (for simplicity).

>>>>

\section{Philosophical objections to counterfactuls}
from the information available to the agent, the joint distribution over counterfactuals cannot be inferred, unless the assignment mechanism in noiseless - so it does not make sense to define regret that depends on it.

There are complex philosophical objections to counterfactuals arising from the way they describe alternate universes that were never realised. This makes it quite easy to (accidentally) make statements about counterfactuals that cannot be tested with empirical data. Consider the following example based on \citet{Dawid2000}. Again we have a drug where the outcome for an individual if treated is represented by the counterfactual variable $\cf{Y}{1}$ and the outcome if not treated is $\cf{Y}{0}$. Suppose these counterfactual variables $\cf{Y}{1}$ and $\cf{Y}{0}$ are jointly normal with equal variance (for simplicity).
